---
title: "Assignment5"
author: "Max Kneißler"
date: "28 1 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(rrot.dir = "C:/Users/user/Desktop/Uni Tuebingen",
      "/Masterstudium/1. Semester/Data Science Project Management/Assignment5")
```

## Introduction

The goal of this assignment to use a public Github repository to improve the
version control system and to manage the development history of this project
carefully. We will interact with the API of ticketmaster.com in a basic and an
advanced way to obtain data from event venues in Germany. We will make use of
this data by plotting a map of Germany, indicating the event locations in
Germany. In addition, this procedure is repeated for another European country.
I was working together with Elias Rudolph (Student ID: 5629871) and Nicolas 
Mollier (Student ID: 5640171)in this assignment to deepen the exchange about 
API and GitHub.

My public repository can be found by:
https://github.com/maxkneissler/Assignment5

To solve the assignment, the following packages are needed:

```{r library, warning = FALSE, message = FALSE}
library(jsonlite)
library(httr)
library(rlist)
library(tidyverse)
library(naniar)
library(ggplot2)
```


## Exercise 1: Setting up a new GitHub repository

As I have not used GitHub before, I created an account and set up a repository
`Assignment5`, which can be accessed by the link presented in the introductory
part. In the following, when dealing with API requests, GitHub allows us to 
have a more efficient version control system. Through the local as well as the 
remote repository, we can access earlier versions easily if the results were not
desirable. Additionally, in case of computer problems, we know that the entire
history of the project is outsourced and can be easily accessed again by logging
into the Github account. Another benefit will not be used in this project, as 
I will not truely collaborate with a colleague. However, it is advisable to use
GitHub in collaborative projects to avoid miscommunications. 

I will proceed by staging smaller steps but committing just parts with a 
meaningful process such that the development history is not too crowded and 
the steps are comprehensive. Next, we will familiarize ourselves with the API 
structure of ticketmaster.com.  






